R-LIME\@: Rectangular Constraints and Optimization for Local Interpretable Model-agnostic Explanation Methods

### 2024-06-27 paper.tex
feat: add reviewers' comments

% typeset the header of the contribution
\maketitle              %

>>>>

\section*{Reviewer Response}
\subsection*{Reviewer \#1}
Suggestions for Rebuttal:
\begin{enumerate}
  \setlength{\itemsep}{15pt}
  \item Offer guidance on how to select optimal parameters for different
        datasets and models.
  \item Include a discussion of other model-agnostic interpretability methods,
        such as SHAP, to provide a more comprehensive overview.

        \vspace{10pt}
        \hspace{.02\textwidth}
        \begin{minipage}{.92\textwidth}%
          Thank you for your suggestion. We added an overview of other
          model-agnostic interpretability methods to the related work section.
        \end{minipage}

  \item Add experimental comparisons with more other model-agnostic \\
        interpretability methods to better evaluate R-LIME's effectiveness.
\end{enumerate}

\subsection*{Reviewer \#4}
The authors should kindly explain why there is not a quantitative comparison
between their proposed method R-LIME and Anchor. The lack of the comparison
makes it hard to evaluate the impact of the proposed model.

\subsection*{Reviewer \#5}
\begin{itemize}
  \setlength{\itemsep}{15pt}
  \item It would be beneficial to move the comparison of R-LIME with Anchor
        and LIME to the Related Work section for improved clarity and
        organization.
  \item The authors should consider exploring a more compatible method than the
        KL-LUCB algorithm to achieve higher accuracy. Although the experimental
        results suggest a minor effect, there may be potential underlying issues
        that need to be addressed.
  \item The title of the `Challenges and Future Work' section could be more
        aptly replaced with `Discussion' to better reflect the content.
\end{itemize}

% typeset the header of the contribution
\maketitle
